\textbf{SPECFEM3D Cartesian}\\ \textbf{User Manual}

### 2014-08-12 doc/USER_MANUAL/manual_SPECFEM3D_Cartesian.tex
switched to the new version of src/shared/utm_geo.f90 in order to have support for the Southern hemisphere. Also switched to the WGS84 ellipsoid instead of Clarke 1866. Updated the users manual accordingly.

>>>>

Use a negative zone number for the Southern hemisphere:
the Northern hemisphere corresponds to zones +1 to +60,
the Southern hemisphere to zones -1 to -60.
We use the WGS84 (World Geodetic System 1984) reference ellipsoid for the UTM projection. If you prefer to use the Clarke 1866 ellipsoid,
edit file \texttt{src/shared/utm\_geo.f90}, uncomment that ellipsoid and recompile the code.
From http://en.wikipedia.org/wiki/Universal\_Transverse\_Mercator\_coordinate\_system :
The Universal Transverse Mercator coordinate system was developed by the United States Army Corps of Engineers in the 1940s.
The system was based on an ellipsoidal model of Earth. For areas within the contiguous United States
the Clarke Ellipsoid of 1866 was used. For the remaining areas of Earth, including Hawaii, the International Ellipsoid was used.
The WGS84 ellipsoid is now generally used to model the Earth in the UTM coordinate system,
which means that current UTM northing at a given point can be 200+ meters different from the old one.
For different geographic regions, other datum systems (e.g.: ED50, NAD83) can be used.
